Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-19 paper/structureScene.tex
PhD -> Ph.D. in Joakim's and Mathieu's biographies

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/anden}}]{Joakim And\'en}
received the M.Sc. degree in mathematics from the Universit\'e Pierre et Marie Curie, Paris, France, in 2010 and the PhD degree in applied mathematics from Ecole Polytechnique, Palaiseau, France, in 2014. He is currently a postdoctoral researcher with the Program in Applied and Computational mathematics at Princeton University, Princeton, USA. His research interests include signal processing, machine learning, and statistical data analysis. He is a member of the IEEE.

@@

\begin{IEEEbiography}[{\includegraphics[width=1.25in,height=1.25in,clip,keepaspectratio]{gfx/lagrange}}]{Mathieu Lagrange} is a CNRS research scientist at IRCCyN, a French laboratory dedicated to cybernetics. He obtained his PhD in computer science at the University of Bordeaux in 2004, and visited several institutions in Canada (University of Victoria, McGill University) and in France (Orange Labs, TELECOM ParisTech, Ircam). His research focuses on machine listening algorithms applied to the analysis of musical and environmental audio.
\end{IEEEbiography}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/anden}}]{Joakim And\'en}
received the M.Sc. degree in mathematics from the Universit\'e Pierre et Marie Curie, Paris, France, in 2010 and the Ph.D. degree in applied mathematics from Ecole Polytechnique, Palaiseau, France, in 2014. He is currently a postdoctoral researcher with the Program in Applied and Computational mathematics at Princeton University, Princeton, USA. His research interests include signal processing, machine learning, and statistical data analysis. He is a member of the IEEE.

@@

\begin{IEEEbiography}[{\includegraphics[width=1.25in,height=1.25in,clip,keepaspectratio]{gfx/lagrange}}]{Mathieu Lagrange} is a CNRS research scientist at IRCCyN, a French laboratory dedicated to cybernetics. He obtained his Ph.D. in computer science at the University of Bordeaux in 2004, and visited several institutions in Canada (University of Victoria, McGill University) and in France (Orange Labs, TELECOM ParisTech, Ircam). His research focuses on machine listening algorithms applied to the analysis of musical and environmental audio.
\end{IEEEbiography}
